---
title: "Creating graphs in R with `ggplot2`"
author: "Michael Kent"
date: "04/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Setting up tools we need
library(tidyverse)
library(readxl)
library(here)
```
# Got to
### https://rstudio-conf-2020.github.io/r-for-excel/ggplot2.html
# Part 5.7

# Plots with ggplot2

We are going to make plots in R and it's going to be amazing.

```{r datainput}
# Reading data in
ca_np <- read_csv(here("data", "ca_np.csv"))
ci_np <- read_excel(here("data", "ci_np.xlsx"))
```

```{r firstplot}
# Basic plot of CI data
gg_base <- ggplot(data = ci_np, aes(x = year, y = visitors)) 
gg_base + geom_point() +
geom_point(color = "purple",
             pch = 25,
             size = 3,
             alpha = 0.5)
#  To use variables for parameters...
#  geom_point(
#    aes(size = visitors,
#        color = visitors),
#    alpha = 0.5
#  )

```

Some common arguments we’ll use first are:

    color = or colour =: update point or line colors
    fill =: update fill color for objects with areas
    linetype =: update the line type (dashed, long dash, etc.)
    pch =: update the point style
    size =: update the element size (e.g. of points or line thickness)
    alpha =: update element opacity (1 = opaque, 0 = transparent)

Building on our first line graph, let’s update the line color to “purple” and make the line type “dashed”:


# Got to
### https://rstudio-conf-2020.github.io/r-for-excel/ggplot2.html
# Part 5.7