---
title: "Creating graphs in R with `ggplot2`"
author: "Michael Kent"
date: "04/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Setting up tools we need
library(tidyverse)
library(readxl)
library(here)
```
# Got to
### https://rstudio-conf-2020.github.io/r-for-excel/ggplot2.html
# Part 5.7

# Plots with ggplot2

We are going to make plots in R and it's going to be amazing.

```{r datainput}
# Reading data in
ca_np <- read_csv(here("data", "ca_np.csv"))
ci_np <- read_excel(here("data", "ci_np.xlsx"))
```

```{r firstplot}
# Basic plot of CI data
gg_base <- ggplot(data = ci_np, aes(x = year, y = visitors)) 
gg_base + geom_point() +
#geom_point(color = "purple",
#             pch = 25,
#             size = 3,
#             alpha = 0.5)
#  To use variables for parameters...
#  geom_point(
#    aes(size = visitors,
#        color = visitors),
#    alpha = 0.5
#  ) +
 theme_bw()

```

Some common arguments we’ll use first are:

    color = or colour =: update point or line colors
    fill =: update fill color for objects with areas
    linetype =: update the line type (dashed, long dash, etc.)
    pch =: update the point style
    size =: update the element size (e.g. of points or line thickness)
    alpha =: update element opacity (1 = opaque, 0 = transparent)

Building on our first line graph, let’s update the line color to “purple” and make the line type “dashed”:

```{r secondplot}

gg_base +
  geom_line(linetype = "dotted") +
  theme_bw() +
  labs(
    x = "Year",
    y = "Annual park visitors",
    title = "Channel Islands NP Visitation",
    subtitle = "(1963 - 2016)"
  )

```
Note: If you want to update the formatting of axis values (for example, to convert to comma format instead of scientific format above), you can use the scales package options (see more from the R Cookbook).
```{r thirdplot}
ggplot(data = ca_np, aes(x = year, y = visitors,color = park_name))+ geom_line()
 
```
```{r five}
gg_np <- ggplot(data = ca_np, aes(x = year, y = visitors, group = park_name))
gg_np +
  geom_line(show.legend = FALSE) +
  theme_light() + 
  labs(x = "year", y = "annual visitors") +
  facet_wrap(~ park_name)
ggsave(here("figures", "np_graph.jpg"), dpi = 180, width = 8, height = 7)
```


# Got to
### https://rstudio-conf-2020.github.io/r-for-excel/ggplot2.html
# Part 5.7